Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-17 analysis/usage.Rmd
some progress

```{r select-columns, message=TRUE, warning=FALSE, include=FALSE}
E_raw %>% select(
  run_package = package, #      The package which was run to trigger the eval
  ev_variant = eval_function, # Which eval variant was called
  duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
  src_ref = eval_call_srcref, # Source ref for the eval call site
  file, #                       Script file name (name of this run)
  ev_package = eval_source, #   Package of the call site
  arg_size = expr_expression_length, # Size in bytes of eval argument string
  opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
) -> E #                               interpreter during eval (non-recursive).

@@

```{r eval-calls-violin-plot}
eval_calls_per_package %>%
  ggplot(aes(x = "", y = n, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Eval calls per package") +
  theme(legend.position = "none")

@@

# Amount of code loaded by eval

@@

r("median size eval", med_size)
r("max size eval", max_size)
r("average size eval", average_size)
r("size nine five", nb_nodes_many$arg_size)
r("size nine five exact percent", percent(nb_nodes_many$cumulative))
```

>>>>

```{r select-columns, message=TRUE, warning=FALSE, include=FALSE}
E_raw %>% select(
  run_package = package, #      The package which was run to trigger the eval
  ev_variant = eval_function, # Which eval variant was called
  duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
  src_ref = eval_call_srcref, # Source ref for the eval call site
  file, #                       Script file name (name of this run)
  ev_package = eval_source, #   Package of the call site
  arg_size = expr_resolved_length, #   Size in bytes of eval argument string
  opcodes = direct_interpreter_eval #  Count of the AST nodes traversed by the
) -> E #                               interpreter during eval (non-recursive).

@@

```{r eval-calls-violin-plot}
sites_per_package %>%
  ggplot(aes(x = "", y = n, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Eval calls per package") +
  theme(legend.position = "none")

@@

# Amount of code

How much code is loaded by eval, we look at argument sizes.

@@

overview_table(
  r("median size eval", med_size),
  r("max size eval", max_size),
  r("average size eval", average_size),
  r("size nine five", nb_nodes_many$arg_size),
  r("size nine five exact percent", percent(nb_nodes_many$cumulative))
) -> TBL

E %>% filter(is.na(arg_size) == FALSE) %>%
  filter(arg_size > 100) %>%
  ggplot(aes(x=arg_size)) + geom_histogram(binwidth=1) 
```

### 2020-12-17 paper/main.tex
some progress

%%%%%
\section{Usage Metrics}

@@

\begin{figure}[h]\begin{tabular}{|r|r|r|r|r|}\hline
   &\eval & \c{evalq} & \c{eval} & \c{local} \\[-2mm]
           & & & \c{.parent} & \\\hline
Static sites & \Staticeval & \Staticevalq & \Staticevalparent & \Staticlocal \\
Exercised sites & \Triggeredeval & \Triggeredevalq & \Triggeredevalparent & \Triggeredlocal \\
Invocations & \EvalsRnd & \EvalqsRnd & \EparentsRnd & \LocalsRnd \\\hline
\end{tabular}\caption{Variants}\label{tab:variantseval}
\end{figure}

@@

\mypara{The case of CORE libraries} ... \NOTE{Give numbers for the
  same things as above but for the base/core libraries} Compare.
\NOTE{Add XXX016 to XXX025.}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Usage Metrics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}[h]\begin{tabular}{|r|r|r|r|r|}\hline
  &\eval & \c{evalq} & \c{eval} & \c{local}\\[-2mm]
           & & & \c{.parent} &\\\hline
Static sites &\Staticeval&\Staticevalq&\Staticevalparent&\Staticlocal \\
Exercised sites&\Triggeredeval&\Triggeredevalq&\Triggeredevalparent&\Triggeredlocal\\
Invocations&\EvalsRnd&\EvalqsRnd&\EparentsRnd&\LocalsRnd\\\hline
\end{tabular}\caption{Variants}\label{tab:variantseval}
\end{figure}

@@
